### 2020-05-26 writeup/proof_main.tex
restructure appendix;

\subsection{Proofs for Section \ref{sec_main}}\label{app_proof_main}

@@

\subsubsection{Proof of Theorem \ref{thm_model_shift}}\label{sec_pfmain}

@@

\subsubsection{Proof of Theorem \ref{thm_many_tasks}}\label{app_proof_many_tasks}

>>>>

\subsection{Proof of Two Tasks with General Covariance}\label{app_proof_main}

@@

@@

\subsection{Proof of Many Tasks with the Same Covariates}\label{app_proof_many_tasks}
